### 2023-08-14 application.tex
up

\section{Resilience for VASS and variations}

@@

\begin{theorem}{}
Resilience is decidable for VASS when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

@@

Resilience is also decidable for other class of counter machines for which the reachability relation can be expressed in a decidable logic. Recall that lossy counter machines \cite{DBLP:conf/rp/Schnoebelen10} are counter machines that may loose tokens in each control-state.

\begin{theorem}{}
Resilience is decidable for lossy counter machines when $\Safe$ and $\Bad$ are semilinear.
\end{theorem}

@@

\begin{theorem}{}
Resilience is decidable for integer VASS when $\Safe$ and $\Bad$ are semilinear.
\end{theorem}

@@

\begin{theorem}\label{RP VASS}
Resilience is decidable for continuous VASS when $\Safe$ and $\Bad$ are definable in the existential theory of
the rationals with addition and order.
\end{theorem}

>>>>

\section{Resilience for VASS and variations}\label{section VASS}

@@

\begin{theorem}{}
{\sc Resilience} is decidable for VASS when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

@@

{\sc Resilience} is also decidable for other class of counter machines for which the reachability relation can be expressed in a decidable logic. Recall that lossy counter machines \cite{DBLP:conf/rp/Schnoebelen10} are counter machines that may loose tokens in each control-state.

\begin{theorem}{}
{\sc Resilience} is decidable for lossy counter machines when $\Safe$ and $\Bad$ are semilinear.
\end{theorem}

@@

\begin{theorem}{}
{\sc Resilience} is decidable for integer VASS when $\Safe$ and $\Bad$ are semilinear.
\end{theorem}

@@

\begin{theorem}\label{RP VASS}
{\sc Resilience} is decidable for continuous VASS when $\Safe$ and $\Bad$ are definable in the existential theory of
the rationals with addition and order.
\end{theorem}
